Measurement Bias from Address Aliasing

### 2016-01-07 paper.tex
Make code compacting change consistent

Overall, it seems reasonable to conclude that the resource stalling is causing the slowdown, ultimately generated by false dependencies from address aliasing.
We do not attempt to pinpoint exactly which accesses generates these conflicts, but at a high level the CPU falsely assumes dependencies between \texttt{input[i]} and \texttt{output[i]}.
By manually adjusting the address alignment of one of these buffers, cycle count can be reduced by as much as 50\%.
This is a speedup on top of already aggressive compiler optimization.
% Variations in execution port activity, and in this case increased number of branches executed, is consistent with micro-ops being reissued after the potential conflict is detected.
% We do not attempt to pinpoint exactly which assembly instructions might alias, but one can assume that the processor thinks memory accesses to \texttt{input[i]} potentially conflicts with \texttt{output[i]}.

@@

\subsubsection{Mark buffers with \texttt{restrict}}
In our convolution kernel implementation, the compiler has to account for the fact that input and output pointers might alias, or that the buffers partially overlap.
This limits the extent generated code can keep data in registers without updating the values from memory, as a write to one buffer potentially could invalidate a cached value from the other.
The C99 keyword \emph{restrict} can be used to explicitly tell the compiler that accesses through a pointer does not alias with any other, allowing for more efficient code generation with fewer memory accesses.
\begin{lstlisting}[breaklines=true]
    void conv(int n, const float * restrict input, float * restrict output);
\end{lstlisting}
With this updated function prototype, the compiler is able to move a store instruction out of the inner loop, reducing the number of stores executed by more than 80 \% on optimization level O2.
Alias events is reduced by about 10 million for the default alignment, with a corresponding improvement in cycle count. % File backing this in results

>>>>

Overall, it seems reasonable to conclude that the resource stalling is causing the slowdown, ultimately generated by false dependencies from address aliasing.
We do not attempt to pinpoint exactly which accesses generates these conflicts, but at a high level the CPU falsely assumes dependencies between \texttt{in[i]} and \texttt{out[i]}.
By manually adjusting the address alignment of one of these buffers, cycle count can be reduced by as much as 50\%.
This is a speedup on top of already aggressive compiler optimization.
% Variations in execution port activity, and in this case increased number of branches executed, is consistent with micro-ops being reissued after the potential conflict is detected.
% We do not attempt to pinpoint exactly which assembly instructions might alias, but one can assume that the processor thinks memory accesses to \texttt{input[i]} potentially conflicts with \texttt{output[i]}.

@@

\subsubsection{Mark buffers with \texttt{restrict}}
In our convolution kernel implementation, the compiler has to account for the fact that input and output pointers might alias, or that the buffers partially overlap.
This limits the extent generated code can keep data in registers without updating the values from memory, as a write to one buffer potentially could invalidate a cached value from the other.
The C99 keyword \emph{restrict} can be used to explicitly tell the compiler that accesses through a pointer does not alias with any other, allowing for more efficient code generation with fewer memory accesses.
\begin{lstlisting}[breaklines=true]
    void conv(int n, const float * restrict in, float * restrict out);
\end{lstlisting}
With this updated function prototype, the compiler is able to move a store instruction out of the inner loop, reducing the number of stores executed by more than 80 \% on optimization level O2.
Alias events is reduced by about 10 million for the default alignment, with a corresponding improvement in cycle count. % File backing this in results
